Ceph Parallel File System Evaluation Report

### 2013-08-16 ceph-eval.tex
Address Scott's two questions in the text
1. read should be write. 2. Figure 2 and 3 now have the same Y axis

%% Are the read and write graphs wrong or should the second sentence below be about write
%% instead of read?
The read and write results are summarized in Figures~\ref{fig:xfs-read}
and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
indicates that XFS can get to the peak \hl{read} performance with five SATA LUNs, then there
is a bit of degradation from there. Changes to
the queue depth do not seem to make any obvious difference on the performance.

>>>>

%% Are the read and write graphs wrong or should the second sentence below be about write
%% instead of read?
The read and write results are summarized in Figures~\ref{fig:xfs-read}
and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
indicates that XFS can get to the peak write performance with five SATA LUNs,
then there is a bit of degradation from there. Changes to
the queue depth do not seem to make any obvious difference on the performance.
